Results discussion

### 2024-11-05 pages/results_discussion.qmd
docs(results dicussion): tidied up from rough notes to neater

## ROUGH NOTES TO SORT BELOW

This page has rough notes that are blurry between results / discussion. It is from me reading ove rmy results section and trying to pull out key points or things I want to mention, and trying to group reflections into categories.

## Headlines / key findings / things want to emphasise

**Timings**. Timings varied alot. RESULT: 2h11 to 28h14.

DISCUSS: Variation due to -

* Time consuming:
    * Write code for scenarios/sensitivity analysis
    * Write code for tables/figures
    * Included troubleshooting mismatch parameters, working out how to change code for scenarios, working out appropriate transformations for processing, and which columns to use, and so on.
* The two quickest studies (by a long shot - <4h v.s. all others >12h) I feel were quick as
    * They required very little troubleshooting (didn't need any or only needed alittle coding from me)
    * Also, simplicity too - they had scope of 1 or 5 items - all others had 5 to 17.

What I think were key factors in not being able to fully reproduce some studies (and hence, these are headline findings):

* **Code containing wrong parameters**.
* **Having to write code for (a) scenarios, and (b) to process results (tables, figures, in-text)**
* These related to badges: complete set of materials

**Open license** (badges and STARS) - couldn't do without.

## Other important things to mention

## Other minor things to mention

## Grouping reflections from reproduction and evaluation into categories

### Model structuring and functionality

**feels important for reuse**

* Runnable
* Programmatic
    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
* Don't hard code
* Relative file paths
* Avoid duplication
* Sufficient comments
* Save outputs to file
* Understandable output
    * Data dictionaries (relevant to inputs and outputs).
    * Badges: careful documentation.
* Avoid large file sizes
* Excessive file number
* Instructions on how to run
    * STARS and badges: documentation (sufficient, minimal and step by step)
* Quicker model
    * State memory use
    * State run time
    * STRESS: Run time. Found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository.

@@

* Open license
    * On ALL repositories required
* Unsupported versions

### Study reporting

See above...

@@

Regarding **relationship between reproduction and evaluation**, in terms of article reporting, these feel like the key things. In terms of repository contents, the key things feel like - see above...

@@

Hence, instead of having **study reporting** category or mentioning above, would describe seperately in own section.

>>>>

TODO: TURN INTO DIAGRAM (like have done for analysis pipeline)

* Runnable
* Programmatic
    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
* Don't hard code
* Relative file paths
* Avoid duplication
* Sufficient comments
* Save outputs to file
* Understandable output
    * Data dictionaries (relevant to inputs and outputs).
* Avoid large file sizes
* Excessive file number
* Instructions on how to run
* Quicker model
    * State memory use
    * State run time

These are important for reuse - but also pipeline stuff! As they (a) make reproduction easier and (b) are important when troubleshooting.

* Data dictionaries - Badges: careful documentation
* Instructions on how to run - STARS and Badges: documentation (sufficient, minimal and step by step)
* Run time - STRESS: run time (found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository)

@@

These didn't fit into the two categories above:

* **Open license**
    * On ALL repositories required
* **Unsupported versions**

## Headline findings

Whilst above captures the reflections, I've also pulled out a few **headline** findings.

The four most important things:

1. **Using correct parameters in code**
2. **Including code for all scenarios**
3. **Include code to create tables, figures and in-text results**
4. **Open license**

Why were these the most fundamental?

**Using the code**. Open license  (4) is fundamentally important - can't reuse code without it. In several studies, had to ask authors to add license (all kindly agreed).

**Timing**. Timings varied alot, from 2h11 to 28h14

* Six slower studies (>12h)
    * I think main reasons for time were: troubleshooting wrong parameters (1), writing code for scenarios (2), and creating tables/figures/in-text results (3) (including appropriate transformations, which columns to use, and so on).
    * Scope could be larger (5 to 17 items)
* Two quicker studies (<4h)
    * Both required very little troubleshooting (e.g. only small amount of coding)
    * Scope was also simple (1 or 5 items)

**Reproduction success**. I think main reasons were having wrong parameters (1), not having code for scenarios (2) and not having code for results (3).

* Badges and STARS: open license
* Badges: complete set of materials

## Relationship between reproduction and evaluation

Regarding relationship between reproduction and evaluation, in terms of article reporting, these feel like the key things that impacted reproduction...

### Article

@@

### Repository

@@

## Other things I wanted to mention
